Robust background subtraction in traffic environments

### 2019-02-08 paper/Paper.tex
Correct figures positioning

\subsection*{N}
$N$ represents how many matrices are kept in memory to model the background.
Each of them stores the history of pixels values.
The greater, the more complex background can be handled but at the cost of heavier
computation. At $N=35$, experimental results show that performance saturates.
\begin{figure*}[!t]
\centering
\subfloat[][N = 2]{
    \includegraphics[width=0.32\textwidth]{Figures/N2.jpg}
    %\label{fig:N2}
}
\subfloat[][N = 10]{
    \includegraphics[width=0.32\textwidth]{Figures/N10.jpg}
}
\subfloat[][N = 20]{
    \includegraphics[width=0.32\textwidth]{Figures/N20.jpg}
}
\caption{We can see the poor mask of the cars on the left road when $N=2$, and the
accurate mask of the lines on the front right when $N=20$.}
\end{figure*}

\subsection*{K}
$K$ tells the number of samples from $B$ that have to be closer than $R$ in order to
classify the pixel as background. The higher, the more difficult for a pixel to be
classified as background.
\begin{figure*}[!t]
\centering
\subfloat[][K = 1]{
    \includegraphics[width=0.32\textwidth]{Figures/K1.jpg}
}
\subfloat[][K = 2]{
    \includegraphics[width=0.32\textwidth]{Figures/K2.jpg}
}
\subfloat[][K = 4]{
    \includegraphics[width=0.32\textwidth]{Figures/K4.jpg}
}
\caption{Setting $K$ too high brings to classify many pixels as foreground, with the risk of false positives.}
\end{figure*}

\subsection*{T max}
$T_max$ controls the lowest probability of updating a pixel and putting it the
background model $B$.

\subsection*{R}
Eq ?????????? is similar to the equation of a pure proportional controller.
In this case the $R(x,y)$ has to follow $d_minavg(x,y) * R_scale$. So:
\begin{itemize}
    \item $R_{incdec}$: setting too high lead to oscillation around the target and if
    set too high leads to divergence. The default value is 0.05 which leads to fast
    enough adaptation to the target value (in more or less 30 frames the target is
    reached). Assuming that the backgroud isnt changing much there is no reason to
    raise it.
    \item $R_{scale}$: tells how much the algorithm is sensitive, in fact it is a direct
    control of the threshold. Setting too high it leads to really few false positives
    but also decreases true positives; setting too low, will increase false positives.
    \item $R_{lower}$: sets a limit on how much $R$ can decrease its value. Setting too
    low, it will lead to a lot of false positives in area that are foreground,
    especially if the video is noise, so especially is zones that are clearly
    background are changing their values of high amounts due to noise. Setting too
    high it will reduce true positives. So the choice of it should be lead by the
    video quality, more than the application domain.
\end{itemize}
\begin{figure*}[!t]
    \centering
    \subfloat[][$R_{scale}$ = 5]{
        \includegraphics[width=0.32\textwidth]{Figures/R_scale5.jpg}
    }
    \subfloat[][$R_{scale}$ = 15]{
        \includegraphics[width=0.32\textwidth]{Figures/R_scale15.jpg}
    }
    \subfloat[][$R_{scale}$ = 50]{
        \includegraphics[width=0.32\textwidth]{Figures/R_scale50.jpg}
    }
\end{figure*}
As we see, as $R_{scale}$ grows the tree leaves that are waved by the wind are not detected
anymore as foreground but also a part of the car is lost.

\subsection*{alpha}
From eq ?????????? we see that alpha tells how much to weight the image gradients
with respect to the image values in the distance computation.
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.45\textwidth]{Figures/gradients.jpg}
    \caption{Gradients}
    \label{fig:gradients}
\end{figure}
As we see, the image gradients give a good cue to distinguish the street from the cars
(image absolute values are not, since many cars have almost the same color of the
street). So alpha should be set high, in order to take into consideration this fact.
But notice that setting too high will lead to noisy masks, especially with noisy
videos that have small variations of the gradient from frame to frame.
\begin{figure*}[!t]
    \centering
    \subfloat[][$\alpha$ = 0]{
        \includegraphics[width=0.32\textwidth]{Figures/alpha0.jpg}
    }
    \subfloat[][$\alpha$ = 10]{
        \includegraphics[width=0.32\textwidth]{Figures/alpha10.jpg}
    }
    \subfloat[][$\alpha$ = 20]{
        \includegraphics[width=0.32\textwidth]{Figures/alpha20.jpg}
    }
    \subfloat[][$\alpha$ = 50]{
        \includegraphics[width=0.32\textwidth]{Figures/alpha50.jpg}
    }
\end{figure*}

>>>>

\subsection*{N}
$N$ represents how many matrices are kept in memory to model the background.
Each of them stores the history of pixels values.
The greater, the more complex background can be handled but at the cost of heavier
computation. At $N=35$, experimental results show that performance saturates.
\begin{figure}[!t]
\centering
\subfloat[][N = 2]{
    \includegraphics[width=0.45\textwidth]{Figures/N2.jpg}
    %\label{fig:N2}
}
\newline
\subfloat[][N = 10]{
    \includegraphics[width=0.45\textwidth]{Figures/N10.jpg}
}
\newline
\subfloat[][N = 20]{
    \includegraphics[width=0.45\textwidth]{Figures/N20.jpg}
}
\caption{We can see the poor mask of the cars on the left road when $N=2$, and the
accurate mask of the lines on the front right when $N=20$.}
\end{figure}

\subsection*{K}
$K$ tells the number of samples from $B$ that have to be closer than $R$ in order to
classify the pixel as background. The higher, the more difficult for a pixel to be
classified as background.
\begin{figure}[!t]
\centering
\subfloat[][K = 1]{
    \includegraphics[width=0.45\textwidth]{Figures/K1.jpg}
}
\newline
\subfloat[][K = 2]{
    \includegraphics[width=0.45\textwidth]{Figures/K2.jpg}
}
\newline
\subfloat[][K = 4]{
    \includegraphics[width=0.45\textwidth]{Figures/K4.jpg}
}
\caption{Setting $K$ too high brings to classify many pixels as foreground, with the risk of false positives.}
\end{figure}

\subsection*{T max}
$T_{max}$ controls the lowest probability of updating a pixel and putting it the
background model $B$.

\subsection*{R}
Eq ?????????? is similar to the equation of a pure proportional controller.
In this case the $R(x,y)$ has to follow $d_{minavg}(x,y) * R_{scale}$. So:
\begin{itemize}
    \item $R_{incdec}$: setting too high lead to oscillation around the target and if
    set too high leads to divergence. The default value is 0.05 which leads to fast
    enough adaptation to the target value (in more or less 30 frames the target is
    reached). Assuming that the backgroud isnt changing much there is no reason to
    raise it.
    \item $R_{scale}$: tells how much the algorithm is sensitive, in fact it is a direct
    control of the threshold. Setting too high it leads to really few false positives
    but also decreases true positives; setting too low, will increase false positives.
    \item $R_{lower}$: sets a limit on how much $R$ can decrease its value. Setting too
    low, it will lead to a lot of false positives in area that are foreground,
    especially if the video is noise, so especially is zones that are clearly
    background are changing their values of high amounts due to noise. Setting too
    high it will reduce true positives. So the choice of it should be lead by the
    video quality, more than the application domain.
\end{itemize}
\begin{figure}[!t]
    \centering
    \subfloat[][$R_{scale}$ = 5]{
        \includegraphics[width=0.45\textwidth]{Figures/R_scale5.jpg}
    }
    \newline
    \subfloat[][$R_{scale}$ = 15]{
        \includegraphics[width=0.45\textwidth]{Figures/R_scale15.jpg}
    }
    \newline
    \subfloat[][$R_{scale}$ = 50]{
        \includegraphics[width=0.45\textwidth]{Figures/R_scale50.jpg}
    }
\end{figure}
As we see, as $R_{scale}$ grows the tree leaves that are waved by the wind are not detected
anymore as foreground but also a part of the car is lost.

\subsection*{alpha}
From eq ?????????? we see that alpha tells how much to weight the image gradients
with respect to the image values in the distance computation.
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.45\textwidth]{Figures/gradients.jpg}
    \caption{Gradients}
    \label{fig:gradients}
\end{figure}
As we see, the image gradients give a good cue to distinguish the street from the cars
(image absolute values are not, since many cars have almost the same color of the
street). So alpha should be set high, in order to take into consideration this fact.
But notice that setting too high will lead to noisy masks, especially with noisy
videos that have small variations of the gradient from frame to frame.
\begin{figure}[!t]
    \centering
    \subfloat[][$\alpha$ = 0]{
        \includegraphics[width=0.45\textwidth]{Figures/alpha0.jpg}
    }
    \newline
    \subfloat[][$\alpha$ = 10]{
        \includegraphics[width=0.45\textwidth]{Figures/alpha10.jpg}
    }
    \newline
    \subfloat[][$\alpha$ = 20]{
        \includegraphics[width=0.45\textwidth]{Figures/alpha20.jpg}
    }
    \newline
    \subfloat[][$\alpha$ = 50]{
        \includegraphics[width=0.45\textwidth]{Figures/alpha50.jpg}
    }
\end{figure}
